\huge{ \emph{Supplement to} Algorithms For Shaping a Particle Swarm\\ With a Shared Control Input Using Boundary Interaction}

### 2016-09-02 RA-L/simulation.tex
One small edit to section
added references to code

Two simulations were implemented using wall-friction for position control.  The first controls the position of two robots, the second controls the position of $n$ robots.  All code is available online at [link withheld for review].

@@

In the worse case, adjusting both $\Delta r_x$ and $\Delta r_y$ requires two iterations.   Two iterations of Alg. \ref{alg:XControl} are only required if $|\Delta e_x - \Delta s_x|>L$. 
Similarly,  two iterations %of Alg. \ref{alg:YControl} 
are only required if $|\Delta e_y - \Delta s_y|>L$.

@@

\subsection{Position Control of $n$ Robots}
Alg. \ref{alg:PosControlNRobots}  was simulated in {\sc Matlab} using square block robots with unity width.
Simulation results are shown in Fig.~\ref{fig:4diagramsplots.pdf} for arrangements with an increasing number of robots,  $n$= [8, 46, 130, 390, 862]. 
The distance moved grows quadratically with the number of robots $n$. A best-fit line $210 n^2 + 1200n-10,000$ is overlaid by the data..

@@

 144 disc-shaped robots were also controlled by a closed-loop controller using the procedure in Section \ref{subsec:ClosedLoopCovarianceControl}. Fig. \ref{fig:CovVarControlPlot} illustrates that covariance and variances in $x$ and $y$ axis were controlled from a set of initial conditions.
\begin{figure}
\begin{center}
	\includegraphics[width=1.0\columnwidth]{CovVarControlPlot2.eps}
\end{center}
\vspace{-1em}
\caption{\label{fig:CovVarControlPlot}
Closed-loop simulation with 144 disc robots and three sets of initial conditions.  The algorithm tracks goal variance and covariance values (green).  The goal covariance switches sign every 30 s.}
\end{figure}

>>>>

Two simulations were implemented using wall-friction for position control.  The first controls the position of two robots, the second controls the position of $n$ robots.  All code is available online at \citet{Zhao2016mathematica,Zhao2016mathematicaSquare}.

@@

In the worse case, adjusting both $\Delta r_x$ and $\Delta r_y$ requires two iterations.   Two iterations of Alg. \ref{alg:XControl} are only required if $|\Delta e_x - \Delta s_x|>L$. 
Similarly,  two iterations %of Alg. \ref{alg:YControl} 
are only required if $|\Delta e_y - \Delta s_y|>L$. An online interactive demonstration and source code of the algorithm are available at \citet{Shahrokhi2015mathematicaParticle}.

@@

\subsection{Position Control of $n$ Robots}
Alg. \ref{alg:PosControlNRobots}  was simulated in {\sc Matlab} using square block robots with unity width. Code is available at \citet{Arun2015}.
Simulation results are shown in Fig.~\ref{fig:4diagramsplots.pdf} for arrangements with an increasing number of robots,  $n$= [8, 46, 130, 390, 862]. 
The distance moved grows quadratically with the number of robots $n$. A best-fit line $210 n^2 + 1200n-10,000$ is overlaid by the data..

@@

 144 disc-shaped robots were also controlled by a closed-loop controller using the procedure in \S \ref{subsec:ClosedLoopCovarianceControl}. Fig. \ref{fig:CovVarControlPlot} illustrates that covariance and variances in $x$ and $y$ axis were controlled from a set of initial conditions.
\begin{figure}
\begin{center}
	\includegraphics[width=1.0\columnwidth]{CovVarControlPlot2.eps}
\end{center}
\vspace{-1em}
\caption{\label{fig:CovVarControlPlot}
Closed-loop simulation with 144 disc robots and three sets of initial conditions.  The algorithm tracks goal variance and covariance values (green).  The goal covariance switches sign every 30 s.}
\end{figure}
